An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data

### 2019-03-22 paper/main.tex
WIP paper and corrmats notebook

\section*{Methods}
There are two basic steps to our approach.  In the first step, we take
a number-of-timepoints ($T$) by number-of-features ($F$)
\textit{matrix of observations} ($\mathbf{X}$) and we return a $T$ by
$\frac{F^2 - F}{2}$ \textit{matrix of dynamic correlations}
($\mathbf{Y}$).  Here $\mathbf{Y_0}$ describes, at each moment, how
all of the features (columns of $\mathbf{X}$) are inferred to be
interacting.  (Since the interactions are assumed to be non-recurrent
and symmetric, only the upper triangle of the full correlation matrix
is computed.)  In the second step, we project $\mathbf{Y_0}$ onto an
$F$-dimensional space, resulting in a new $T$ by $F$ matrix
$\mathbf{Y_1}$.  Note that $\mathbf{Y_1}$ contains information about
the correlation dynamics present in $\mathbf{X}$, but represented in a
compressed number of dimensions.  By repeatedly applying these two
steps in sequence, we can examine and explore higher order dynamic
correlations in $\mathbf{X}$.

@@

\subsubsection*{Generating synthetic data}
Ramping dataset and block dataset.  Create an example figure for both.

>>>>

\section*{Methods}
There are two basic steps to our approach (Fig.~\ref{fig:methods_fig}).  In the first step, we take
a number-of-timepoints ($T$) by number-of-features ($F$)
\textit{matrix of observations} ($\mathbf{X}$) and we return a $T$ by
$\frac{F^2 - F}{2}$ \textit{matrix of dynamic correlations}
($\mathbf{Y}$).  Here $\mathbf{Y_0}$ describes, at each moment, how
all of the features (columns of $\mathbf{X}$) are inferred to be
interacting.  (Since the interactions are assumed to be non-recurrent
and symmetric, only the upper triangle of the full correlation matrix
is computed.)  In the second step, we project $\mathbf{Y_0}$ onto an
$F$-dimensional space, resulting in a new $T$ by $F$ matrix
$\mathbf{Y_1}$.  Note that $\mathbf{Y_1}$ contains information about
the correlation dynamics present in $\mathbf{X}$, but represented in a
compressed number of dimensions.  By repeatedly applying these two
steps in sequence, we can examine and explore higher order dynamic
correlations in $\mathbf{X}$.

@@

\subsubsection*{Generating synthetic data}
Ramping dataset and block dataset. Add details (Fig.~\ref{fig:synthetic_data})
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
  \caption{\textbf{Dynamic correlation recovery with synthetic data.
      a.Recovery using a constant dataset.} Using constant dataset,
    how well can we recover using different
    kernels. \textbf{b. Recovery using random dataset.}
    \textbf{c. Ramping recovery.}  \textbf{d. Block recovery} blah}
  \label{fig:synthetic_data}
\end{figure}
